Dominance Regions for Imaginary $\bfg$-vectors

### 2020-06-08 dominance_regions.tex
Limit statement
Inequalities

  Define Chebyshev polynomials $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]

>>>>

  Define Chebyshev polynomials $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  \begin{lemma}
    For $i\ge1$ and any $\varepsilon$, we have $u_{i,\varepsilon}>0$ and $u_{i-1,\varepsilon}u_{i+1,-\varepsilon}<u_{i,\varepsilon}u_{i,-\varepsilon}$.
    Moreover,
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}\]
  \end{lemma}
  \begin{proof}
    We prove the inequalities by induction, the base case $i=1$ being clear from the definitions.
    Without loss of generality, assume $\varepsilon=+$.
    For $i>1$, we have 
    \[u_{i-1,\varepsilon}u_{i+1,-\varepsilon}=cu_{i-1,\varepsilon}u_{i,\varepsilon}-u_{i-1,\varepsilon}u_{i-1,-\varepsilon}<cu_{i-1,\varepsilon}u_{i,\varepsilon}-u_{i-2,-\varepsilon}u_{i,\varepsilon}=u_{i,-\varepsilon}u_{i,\varepsilon},\]
    where the inequality follows by induction.

    Thus we see that the sequence $\frac{-u_{i,-}}{u_{i-1,+}}$ is increasing and the sequence $\frac{-u_{i-1,-}}{u_{i,+}}$ is decreasing.
    As the first is bounded above by $\frac{-1}{b}$ and the second is bounded below by $-c$, they both converge.
  \end{proof}
